---
title: "R Notebook"
output: html_notebook
---
Q2. 

Analysis of Canadian Manufacturing Workers Work-Hours: The time series plot below describes the average annual number of weekly hours spent by Canadian manufacturing workers. The data is available in CanadianWorkHours.xls.

(a) Reproduce the time plot

```{r}
# identify the current location of the r-file and set it as the working directory
  
setwd(getwd())


# Loading
library("readxl")

library(ggplot2)



# Read data into R
work_hours = read_excel("CanadianWorkHours.xls", sheet = "Sheet1")


# print(work_hours)

ggplot(work_hours, aes(x=work_hours$`Year`, y=work_hours$`Hours per week`))+
  ylim(34, 38) +
  geom_line( color="#69b3a2", size=1, alpha=0.9, linetype=1) +
  ggtitle("Canadian Manufacturing Work Hours") +
  xlab("Year") +
  ylab("Hours per week") + 
  ylim(breaks = c(34.5, 35,36,37,38))
  

```
Q3. a

```{r}
setwd(getwd())

# Read the data
caschool = read.csv(file = 'caschool.csv')
# print(caschool)
print("Summary Statistics for students’ test score" )
summary(caschool$testscr)

print("Summary Statistics for the student-teacher ratio")
summary(caschool$str)

```
Q3.b) Run a regression of testscr on str. List the regression results. Use a sentence to interpret the regression coefficient of str.

Interpretation: 

The regression line can be written as testscr = 698.93 - 2.28 str. 

The regression coefficient for str is -2.25. It means that for every extra if the students to teachers ration increases by 1 then the test score reduces by -2.28 units.

```{r}
print("This is the correlation coefficients:") 

cor(caschool$testscr, caschool$str)

print("This is where we calculate the linear regression model")
model <- lm(testscr ~ str, data = caschool)

print("This is the coefficient and the intercept of the Linear Regression Model")
model
```
Q3.(c) Use a sentence to interpret the R-squared

Interpretation: The model has an udjusted R-squared of 0.0898. The implication is that 4% of the change in students scores can be explained by a change in the students to teachers ratio.

```{r}
print("This is the summary of the linear regression model. This is where we find the R-squared")
summary(model)
```
Q3. (d) Draw a graph of testscr versus str. Add a regression fitted line on the graph.


```{r}
ggplot(caschool, aes(x = str, y = testscr)) +
  geom_point() +
  stat_smooth(method = lm, se = FALSE)


```
Q3 (e) Draw a graph of regression residuals versus str. Add a horizontal line on the graph.

```{r}
str_residuals = resid(model)

plot(caschool$str, str_residuals, ylab = "Rediduals", xlab = 'student-teacher ratio', main = "Residuals due to Students Teacher Ratio")+
  abline(0,0)
```

